A Survey on Ordered Binary Decision Diagrams

### 2015-09-10 paper.tex
Add citations
Add paragraphs (definitions)

As the name suggests, \textit{Reduced} Ordered Binary Decision Diagrams are a 
minimized representation of BDDs. Furthermore, the decision variables are ordered
consistently. More formally, for any node $\upsilon$ and their respective children
$\omega_1$ and $\omega_2$, a total ordering is imposed, i.e.
$var(\upsilon) < var(\omega_1)$ and $var(\upsilon) < var(\omega_2)$, respectively,
where $var(x)$ denotes the label of node $x$.

@@

>>>>

As the name suggests, \textit{Reduced} Ordered Binary Decision Diagrams are a 
minimized representation of BDDs. Furthermore, the decision variables are ordered
consistently. More formally, for any node $\upsilon$ and their respective children
$\omega_1$ and $\omega_2$, a total ordering is imposed, i.e.
$var(\upsilon) < var(\omega_1)$ and $var(\upsilon) < var(\omega_2)$, respectively,
where $var(x)$ denotes the label of node $x$~\cite{BRYANT86, BRYANT92}.

@@

Before discussing the reduction procedure, some definitions are necessary. Here
the original definitions of Bryant~\cite{BRYANT86, BRYANT91} are reused.

A Boolean function can be represented as an OBDD, i.e. a rooted, directed,
acyclic graph (DAG) with a set of nodes $V$ as well as a set of edges $E$.

There exist \textit{nonterminal} and \textit{terminal} nodes. Each
\textit{nonterminal} node $n$ has its own label $var(n)$ as well as two edges,
connecting it to its left $lo(n)\in V$ and right child $hi(n)\in V$, respectively. 
Each \textit{terminal} node $t$ has a unique value $value(t)$, i.e. $value(t)$
is a constant function (for Boolean functions \textbf{0} or \textbf{1}). Hence,
for each constant function only a single terminal node exists.

The following property has to hold for any nonterminal node $n$ in order to
satisfy the ordering requirement of an OBDD:
$var(n) < var(lo(n)) \land var(n) < var(hi(n))$.
In other words, for any path starting at the root of an OBDD, if a path is
followed until a terminal node is reached, the nonterminal nodes are traversed
strictly in the variable ordering.
